Leveraging Diversity to Find Bugs in JavaScript Engines

### 2019-02-19 paper/paper.tex
revising classifier par.

% (\jsc{}=147, \veight{}=370, and \smonkey{}=110).
% (\jsc{}=\Fix{XX}, \veight{}=\Fix{XX}, \smonkey{}=\Fix{XX})
To obtain test files included as attachments, we wrote a crawler to
visit the issue trackers of all engines listed in
Table~\ref{tab:engines} and we were able to retrieve a total of
\Fix{627} files.  To mine tests from the textual descriptions we
proceeded as follows. First, we broke the text describing the issue in
paragraphs and used a binary classifier to label each paragraph as
``code'' or ``not code'' (\ie{}, natural language). Then, based on
that information, we merged consecutive paragraphs labeled as ``code''
and used a \js\ parser to check well-formedness of the retrieved code
fragment. Using that method we were able to retrieve a total of
\Fix{XX} files. All those files were included in
Table~\ref{tab:test-suites}. For the classification of ``code''
vs. ``not code'', we used word2vec~\cite{kusner2015word}, a popular
NLP technique to produce word embeddings. A word embedding is a
mapping of words---in our case, sentences---to vectors of real
numbers. With that mapping it is possible to measure distance between
two sentences as the distance between the vectors characterizing
them. Consequently, one can measure, for example, the minimum distance
between a sentence in English and a sentence in a \js\ embedding,
built with word2vec using a corpus of \js\ sentences. \Mar{Please
  confirm if this is the idea! If yes, shouldn't just one corpus
  (e.g., the JS corpus) be enough to solve the problem? Are there two
  separate embeddings (one for English and one for JS)? If not, how
  they are combined? What about the classification scheme?  It needs
  to answer yes/no (not a distance).}  We used a corpus with 25K
samples of English paragraphs and 25K snippets of \js{} code and
obtained a classifier with accuracy of 98\%. This classifier is
publicly available from our website as a separate component.

>>>>

% (\jsc{}=147, \veight{}=370, and \smonkey{}=110).
% (\jsc{}=\Fix{XX}, \veight{}=\Fix{XX}, \smonkey{}=\Fix{XX})
To obtain test files included as attachments, we wrote a crawler to
visit the issue trackers of all engines listed in
Table~\ref{tab:engines} and we were able to retrieve a total of
\Fix{627} files.  To mine tests from the textual descriptions we
proceeded as follows. First, we broke the text describing the issue in
paragraphs and used a binary classifier to label each paragraph as
``code'' or ``not code'' (\ie{}, natural language). Then, based on
that information, we merged consecutive paragraphs labeled as ``code''
and used a \js\ parser to check well-formedness of the retrieved code
fragment. Using that method we were able to retrieve a total of
\Fix{XX} files. All those files were included in
Table~\ref{tab:test-suites}.

For the classification of ``code'' vs. ``not code'', we used a
pipeline of two Neural Networks (NN), a popular design for solving NLP
classification problems~\Fix{cite}. The first net in the pipeline
takes as input an arbitrary sentence and produces on output a
characterization vector for that sentence. The second net in the
pipeline takes that vector on input and the class for that attribute
(\ie{}, ``(not) code'') and produces a yes/no answer, determining
whether or not the input sentence was code. More in detail, for the
first net, we used word2vec~\cite{kusner2015word}, a popular NLP
technique to produce word embeddings. A word embedding is a mapping of
words to vectors of real numbers. For the second net, we used a
multi-layer perceptron~\Fix{cite} to infer the probability of the
input belonging or not to the class. We classify as code an input for
which the pipeline produces a probability of 0.7 or higher. We used a
corpus with 25K samples of English paragraphs and 25K snippets of
\js{} code and obtained a classifier with accuracy of 98\%. This
classifier is publicly available from our website as a separate
component.

%% With that mapping it is
%% possible to measure distance between two sentences as the distance
%% between the vectors characterizing them. Consequently, one can
%% measure, for example, the minimum distance between a sentence in
%% English and a sentence in a \js\ embedding, built with word2vec using
%% a corpus of \js\ sentences. \Mar{Please confirm if this is the idea!
%%   If yes, shouldn't just one corpus (e.g., the JS corpus) be enough to
%%   solve the problem? Are there two separate embeddings (one for
%%   English and one for JS)? If not, how they are combined? What about
%%   the classification scheme?  It needs to answer yes/no (not a
%%   distance).}
